### 2018-05-22 latex/sc18/prelims.tex
fixing typos

We use $\circ$ to denote the outer product of two or more vectors.
The Hadamard product is the element-wise matrix product and will be denoted using $\Hada$. 
The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. 
Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. 
It can be thought of as a row-wise Hadamard product, where $\M{K}(i+I_{A}(j{-}1),:) = \M{A}(i,:) \Hada \M{B}(j,:)$, or a column-wise Kronecker product, where $\M{K}(,c) =  \M{A}(:,c) \Kron \M{B}(:,c)$.

@@

The $n$th mode matricized tensor denoted by $\M{A}_{(n)}$ is a $I_n\times I/I_n$ matrix formed by organizing the $n$th mode fibers of a tensor $\T{X}$ with dimensions $I_{1} \times ... \times I_{N}$ (and $I=\prod I_n$) into the columns of a matrix. 
The Matricized-Tensor Times Khatri-Rao Product or MTTKRP will be central to this work and takes the form $\Mn{M}{n} = \Mz{A}{n} \Mn{S}{n}$, where $\Mn{S}{n}= \Mn{H}{N} \Khat \cdots \Khat \Mn{H}{n+1} \Khat \Mn{H}{n-1} \Khat  \cdots \Khat \Mn{H}{1}$.

@@

\begin{algorithm}
%\caption{$(\CPl,\epsilon) = \text{NNCP}(\TA,k)$}
\caption{$\CP = \text{NNCP}(\TA,k)$}
\label{alg:nncp}
\begin{algorithmic}[1]
\Require $\TA$ is $I_1\times \cdots \times I_N$ tensor, $k$ is approximation rank
\State \Comment{Initialize data}
%\State $\alpha = \|\TA\|^2$
\For{$n=2$ to $N$}
	\State Initialize $\Mn{H}{n}$ 
	\State $\Mn{G}{n} = \MnTra{H}{n}\Mn{H}{n}$
\EndFor
\State \Comment{Compute NNCP approximation}
\While{not converged}
	\State \Comment{Perform outer iteration of BCD}
	\For{$n=1$ to $N$}
	\State \Comment{Compute new factor matrix in $n$th mode}
	\State $\Mn{M}{n} = \text{MTTKRP}(\TA,\{\Mn{H}{i}\},n)$
		\label{line:MTTKRP}
	\State $\Mn{S}{n} = \Mn{G}{1} \Hada \cdots \Hada \Mn{G}{n-1} \Hada \Mn{G}{n+1} \Hada \cdots \Hada \Mn{G}{N}$
		\label{line:GH}
	\State $\Mn{H}{n} = \text{NLS-Update}(\Mn{S}{n},\Mn{M}{n})$
		\label{line:NLS}
%	\State $\Mn[\hat]{H}{n} = \text{NLS-Update}(\Mn{S}{n},\Mn{M}{n})$
%	\State \Comment{Normalize columns}
%	\State $\V{\lambda} = \text{Col-Norms}(\Mn[\hat]{H}{n})$
%	\State $\Mn{H}{n} = \text{Col-Scale}(\Mn[\hat]{H}{n},\V{\lambda})$
%	\State \Comment{Organize data for later modes}
	\State $\Mn{G}{n} = \MnTra{H}{n}\Mn{H}{n}$
		\label{line:Gn}
	\EndFor
%	\State \Comment{Compute relative error $\epsilon$ from mode-$N$ matrices}
%	\State $\beta = \langle \Mn{M}{N},\Mn[\hat]{H}{N} \rangle$
%	\State $\gamma = \V{\lambda}^\Tra (\Mn{S}{N} \Hada \Mn{G}{N}) \V{\lambda}$
%	\State $\epsilon = \sqrt{(\alpha-2\beta+\gamma)/\alpha}$ 
\EndWhile
%\Ensure $\|\TA - \dsquare{\V{\lambda}; \Mn{H}{1},\dots,\Mn{H}{N}}\| /\|\TA\| = \epsilon$
\Ensure $\TA \approx \CP$
\end{algorithmic}
\end{algorithm}

>>>>

We use $\circ$ to denote the outer product of two or more vectors.
The Hadamard product is the element-wise matrix product and will be denoted using $\Hada$. 
The Khatri-Rao product, abbreviated KRP, will be denoted with $\Khat$. 
Given matrices $\M{A}$ and $\M{B}$ that are $I_{A} \times R$ and $I_{B} \times R$, the KRP $\M{K} = \M{A} \Khat \M{B}$ is $I_{A}I_{B} \times R$. 
It can be thought of as a row-wise Hadamard product, where $\M{K}(i+I_{A}(j{-}1),:) = \M{A}(i,:) \Hada \M{B}(j,:)$, or a column-wise Kronecker product, where $\M{K}(:,c) =  \M{A}(:,c) \Kron \M{B}(:,c)$.

@@

The $n$th mode matricized tensor denoted by $\M{A}_{(n)}$ is a $I_n\times I/I_n$ matrix formed by organizing the $n$th mode fibers of a tensor $\T{X}$ with dimensions $I_{1} \times ... \times I_{N}$ (and $I=\prod I_n$) into the columns of a matrix. 
The Matricized-Tensor Times Khatri-Rao Product or MTTKRP will be central to this work and takes the form $\Mn{M}{n} = \Mz{A}{n} \Mn{K}{n}$, where $\Mn{K}{n}= \Mn{H}{N} \Khat \cdots \Khat \Mn{H}{n+1} \Khat \Mn{H}{n-1} \Khat  \cdots \Khat \Mn{H}{1}$.

@@

\begin{algorithm}
%\caption{$(\CPl,\epsilon) = \text{NNCP}(\TA,k)$}
\caption{$\CP = \text{NNCP}(\TA,R)$}
\label{alg:nncp}
\begin{algorithmic}[1]
\Require $\TA$ is $I_1\times \cdots \times I_N$ tensor, $R$ is approximation rank
\State \Comment{Initialize data}
%\State $\alpha = \|\TA\|^2$
\For{$n=2$ to $N$}
	\State Initialize $\Mn{H}{n}$ 
	\State $\Mn{G}{n} = \MnTra{H}{n}\Mn{H}{n}$
\EndFor
\State \Comment{Compute NNCP approximation}
\While{not converged}
	\State \Comment{Perform outer iteration of BCD}
	\For{$n=1$ to $N$}
	\State \Comment{Compute new factor matrix in $n$th mode}
	\State $\Mn{M}{n} = \text{MTTKRP}(\TA,\{\Mn{H}{i}\},n)$
		\label{line:MTTKRP}
	\State $\Mn{S}{n} = \Mn{G}{1} \Hada \cdots \Hada \Mn{G}{n-1} \Hada \Mn{G}{n+1} \Hada \cdots \Hada \Mn{G}{N}$
		\label{line:GH}
	\State $\Mn{H}{n} = \text{NLS-Update}(\Mn{S}{n},\Mn{M}{n})$
		\label{line:NLS}
%	\State $\Mn[\hat]{H}{n} = \text{NLS-Update}(\Mn{S}{n},\Mn{M}{n})$
%	\State \Comment{Normalize columns}
%	\State $\V{\lambda} = \text{Col-Norms}(\Mn[\hat]{H}{n})$
%	\State $\Mn{H}{n} = \text{Col-Scale}(\Mn[\hat]{H}{n},\V{\lambda})$
%	\State \Comment{Organize data for later modes}
	\State $\Mn{G}{n} = \MnTra{H}{n}\Mn{H}{n}$
		\label{line:Gn}
	\EndFor
%	\State \Comment{Compute relative error $\epsilon$ from mode-$N$ matrices}
%	\State $\beta = \langle \Mn{M}{N},\Mn[\hat]{H}{N} \rangle$
%	\State $\gamma = \V{\lambda}^\Tra (\Mn{S}{N} \Hada \Mn{G}{N}) \V{\lambda}$
%	\State $\epsilon = \sqrt{(\alpha-2\beta+\gamma)/\alpha}$ 
\EndWhile
%\Ensure $\|\TA - \dsquare{\V{\lambda}; \Mn{H}{1},\dots,\Mn{H}{N}}\| /\|\TA\| = \epsilon$
\Ensure $\TA \approx \CP$
\end{algorithmic}
\end{algorithm}
